Supplementary Information to "Improving Models to Predict Holocellulose and Klason Lignin Contents for Peat Soil Organic Matter with Mid Infrared Spectra

### 2022-03-03 analysis/paper/008-paper-supplementary.Rmd
Update manuscript 1, update formatting fo references.

```{r sup-setup, echo=FALSE}
knitr::opts_chunk$set(fig.align = "center", 
                      fig.pos = "H",
                      echo = FALSE,
                      cache = TRUE,
                      dev = "pdf")
```

@@

```{r res-p-pred-diff-hol-intensity2, warning=FALSE, echo=FALSE, out.width="50%", fig.height=14, fig.width=7, fig.cap='Prediction differences between the original model and improved model using binned spectra for the training (first row), peat (second row), and vegetation (bottom row) samples of \\cite{Hodgkins.2018} for different ranges of \\texttt{carb} peak heights (columns) versus intensities at different wavenumber values on the x axis (a: 3400, b: 1200, c: 1550 cm$^{-1}$). Larger prediction differences mean that the original model made larger predictions than the improved model using binned spectra.'}
p_pred_diff_hol_intensity2
```

>>>>

```{r sup-setup, echo=FALSE}
knitr::opts_chunk$set(fig.align = "center", 
                      fig.pos = "H",
                      echo = FALSE,
                      cache = TRUE,
                      dev = "png")
```

@@

```{r res-p-pred-diff-hol-intensity2, warning=FALSE, echo=FALSE, out.width="50%", fig.height=14, fig.width=7, fig.cap='Prediction differences between the original model and improved model using binned spectra for the training (first row), peat (second row), and vegetation (bottom row) samples of \\cite{Hodgkins.2018} for different ranges of \\texttt{carb} peak heights (columns) versus intensities at different wavenumber values on the x axis (a: 3400, b: 1250, c: 1590 cm$^{-1}$). Larger prediction differences mean that the original model made larger predictions than the improved model using binned spectra.'}
p_pred_diff_hol_intensity2
```
